How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-08-29 paper.tex
acknowledged Tod
incorporated Justin Lemkul's suggestions

In all of these cases, it is necessary to interact with the people who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed. Asking complete strangers for help
is often intimidating, especially the first time you do it. However, the best
way to do so is rarely taught explicitly --- at best, it's something one picks
up by example, from fellow lab members or your PI.  {\emph The goal of this
paper is to reveal the hidden curriculum -- what's expected of a software
consumer, how to ask for help, how to contribute productively to a software
community (regardless of whether you can write code).}

@@

@@

    \item Give steps necessary to reproduce the bug.

@@

This should go without saying, but if you're asking for help it behooves you to
do so respectfully. We're not saying that you need to be obsequious. Rather,
approach every interaction with respect: respect for people's time, respect for
their ideas, respect for their identity (including among other things race,
ethnicity, country, sex or gender, or career stage). If you're asking for help,
do so with the perspective that the developer is volunteering their time to help
you, with minimal payoff to them.  If you're reporting a bug, you're almost
certainly frustrated; try not to take that frustration out on the developers. If
you're offering a new feature, keep in mind that it may not align with the
developers' vision for where the software is going.

@@

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%

>>>>

In all of these cases, it is necessary to interact with the people who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed. Asking complete strangers for help
is often intimidating, especially the first time you do it. However, the best
way to do so is rarely taught explicitly --- at best, it's something one picks
up by example, from fellow lab members or your PI.  \emph{The goal of this
paper is to reveal the hidden curriculum -- what's expected of a software
consumer, how to ask for help, how to contribute productively to a software
community (regardless of whether you can write code).}

@@

Along the same lines, it is often valuable to construct a fake or minimal data
set where the correct answer is known (or easily computed outside the program).
This is particularly important when your concern is for the program's
correctness. This is particularly important when your concern is that the
program is producing incorrect answers due to a coding error or assumptions
incompatible with the input data.

@@

    \item Give steps necessary to reproduce the bug. Include any input data
    required.

@@

This should go without saying, but if you're asking for help it behooves you to
do so respectfully. We're not saying that you need to be obsequious. Rather,
approach every interaction with respect: respect for people's time, respect for
their ideas, respect for their identity (including among other things race,
ethnicity, country, native language, sex or gender, or career stage). If you're
asking for help, do so with the perspective that the developer is volunteering
their time to help you, with minimal payoff to them.  If you're reporting a bug,
you're almost certainly frustrated; try not to take that frustration out on the
developers. If you're offering a new feature, keep in mind that it may not align
with the developers' vision for where the software is going.

@@

It's also important to recognize that even while English has become the default
language for science, not everyone is a native speaker, which means that some
jargon, abbreviations, and idioms may be incomprehensible to a fair portion of
your community. Moreover, an awkwardly worded question often reflects lack of
familiarity with the language rather than laziness or ignorance. It's important
to keep accessibility in mind while creating documentation or interacting with
users in a forum.

@@

\section{Other Contributions}
%%%%%%%%%%%%%%%
% You should include all people who have filed issues that were
% accepted into the paper, or that upon discussion altered what was in the paper.
% Multiple significant contributions might mean that the contributor
% should be moved to authorship at the discretion of the a
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io for
% more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%
Dr. Tod D. Romo reviewed the document for style and content. Dr. Justin Lemkul
made numerous helpful suggestions, particularly regarding language
accessibility.
